---
title: "Super Store Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: ["twitter","facebook","menu"]
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(caret)
library(dplyr)
library(skimr)
library(readxl)
```

```{r}
store <- read_xlsx("SampleSuperstore.xlsx")
store[,1:9]=lapply(store[,1:9], factor)
skim(store)
store$ship=store$`Ship Mode`
```
Exploratory Data Visualization All
=====================================
Row
-----------------------------------------------------------------------

### All Features

```{r}

pairs(store ,panel = panel.smooth)
```

Exploratory Data Visualization 1a
====================================================
Row 
-----------------------------------------------------------------------

### Shiping Modde vs Profit

```{r}
store=store %>% group_by(ship) %>% mutate(nship=n()/nrow(store))
ggplot(store,aes(y=store$Profit,x=store$`Ship Mode`, fill=store$`Ship Mode`))+geom_violin(aes(weight=nship ))
```

### Segment vs Profit

```{r}
store=store %>% group_by(Segment) %>% mutate(nseg=n()/nrow(store))
ggplot(store,aes(y=store$Profit,x=store$Segment,fill=store$Segment))+geom_violin(aes(weight=nseg ))
```

Exploratory Data Visualization 1b
====================================================

### Region vs Profit
```{r}
store=store %>% group_by(Region) %>% mutate(nreg=n()/nrow(store))
ggplot(store,aes(y=store$Profit,x=store$Region,fill=store$Region))+geom_violin(aes(weight=nreg ))
```

### Category vs Profit
```{r}
store=store %>% group_by(Category) %>% mutate(ncat=n()/nrow(store))
ggplot(store,aes(y=store$Profit,x=store$Category,fill=store$Category))+geom_violin(aes(weight=ncat ))
```

EDV 2
=======================================================

Column {data-width=2000}
------------------------------------------------------------------------------------------
### State vs Profit
```{r}
ggplot(store,aes(y=store$Profit,x=store$State))+geom_jitter(aes(col=State ))
```

### Sub category vs Profit
```{r}
ggplot(store,aes(y=store$Profit,x=store$`Sub-Category`))+geom_jitter(aes(col=store$`Sub-Category` ))
```

EDV 3
=======================================

Row
------------------------------------
### Sales vs Profit
```{r}
ggplot(store,aes(y=store$Profit,x=store$Sales))+geom_jitter(aes(col=store$Sales ))
```

### Discount vs Profit
```{r}
ggplot(store,aes(y=store$Profit,x=store$Discount))+geom_jitter(aes(col=store$Discount ))

```


### Quantity vs Profit
```{r}
ggplot(store,aes(y=store$Profit,x=store$Quantity))+geom_jitter(aes(col=store$Quantity ))

```

EDV 4a
=======================================

### Quantity vs Sales
```{r}
ggplot(store,aes(y=store$Sales,x=store$Quantity))+geom_jitter(aes(col=store$Quantity ))

```

###  Discount vs Sales
```{r}
ggplot(store,aes(y=store$Sales,x=store$Discount))+geom_jitter(aes(col=store$Prof ))

```

EDV 4b
=======================================
### Category vs Sales
```{r}
ggplot(store,aes(y=store$Sales,x=store$Category))+geom_jitter(aes(col=store$Profit ))

```

### Sub-Category vs Sales
```{r}
ggplot(store,aes(y=store$Sales,x=store$`Sub-Category`))+geom_jitter(aes(col=store$`Sub-Category` ))

```

EDV 5
=======================================
### Category vs Quantity
```{r}
ggplot(store,aes(y=store$Quantity,x=store$Category))+geom_jitter(aes(col=store$Profit ))

```

### SUb-Category vs Quantity
```{r}
ggplot(store,aes(y=store$Quantity,x=store$`Sub-Category`))+geom_jitter(aes(col=store$`Sub-Category` ))

```